My title

### 2024-03-16 paper/paper.qmd
second model added

@@

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(first_model, "rhat")
```

>>>>

first_model <- 
  readRDS(file = here::here("models/model_1.rds"))

modelsummary::modelsummary(
  list(
    "First Model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

@@

set.seed(853)

data|> 
  slice_sample(n = 1000)

pp_check(model_1) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(model_1) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@
